---
title: "Week 1 Exercises"
author: "Jeremiah Lowhorn"
date: "May 9, 2022"
output: 
    pdf_document:
    toc: true
    theme: united
---

Please complete all exercises below WITHOUT using any libraries/packages.

# Exercise 1
## subheader
### heavily nested
#### 
Assign 10 to the variable x. Assign 5 to the variable y. Assign 20 to the variable z.

```{r ex1}
#your code below
x <- 10
y <- 5
z <- 20

```


# Exercise 2
Show that x is less than z but greater than y.

**Note: your output must be a SINGLE boolean, do not output a boolean for each expression.**

```{r ex2}
#your code below
(x<z)&(x>y)


```

# Exercise 3
Show that x and y do not equal z. 

**Note: your output must be a SINGLE boolean, do not output a boolean for each expression.**

```{r ex3}
#your code here

(x != z) | (y != z)
```


# Exercise 4
Show that the formula `x + 2y = z`. 

**Note: your output must be a SINGLE boolean**

```{r ex4}
#your code below

(x + (2*y)) == z

```

# Exercise 5
I have created a vector (test_vector) of integers for you. Determine if any of x, y, or z are in the vector. 

**Note: your output must be a SINGLE boolean, do not output a boolean for each expression.**


```{r ex5}
test_vector <- c(1,5,11:22)
#your code below
(x %in% test_vector)|(y %in% test_vector)|(z %in% test_vector)


```

# Exercise 6
Show which value is contained in the test vector. To do this you will need to create an element-wise logical vector using operators. `x == vector`. Once you have done that you will need to use slicing to return all indices that have matches.
**Note: your output should be two integers**

```{r ex6}
#your code below
which((x == test_vector)|(y == test_vector)|(z == test_vector))

```

